What is essential?

### 2016-03-15 paper/presentation/presentation.tex
add more stuff

\setbeamertemplate{footline}[frame number]
\title[What is essential?]{What is essential?}
\subtitle{\footnotesize -- A pilot survey on views about the requirements metamodel of reqT.org}
\author{Björn Regnell}
\institute{Lund University}
\date{March 14, 2016\\ \href{http://refsq.org/2016}{refsq.org/2016}\\ \href{https://github.com/bjornregnell/reqT-survey}{github.com/bjornregnell/reqT-survey}}

@@

\item Make a survey among RE scholars
\pause
\begin{itemize}
\item How to quantify ''essentiality''?
\pause
\begin{itemize}
\item One possible quantification: \\ The more scholars that \Emph{agree} on a definition of a concept \\ and \\ the more scholars that \Emph{use} the concept, \\ the more \Alert{essential} is the concept.
\end{itemize}
\end{itemize}
\pause
\item Use the reqT metamodel as a basis for the survey
\end{itemize}
\end{Slide}

\section{Background}
\subsection{About reqT}
\begin{Slide}{What is reqT?}
\begin{itemize}
\item reqT is an open source requirements engineering tool developed in an \Emph{educational} context\\ Download from here: \url{http://reqt.org/} \\ \texttt{java -jar reqT.jar}
\item reqT aims to inspire \Alert{code-loving} cs students to learn more about RE through a \Emph{Scala}-internal DSL
\item reqT has a \Emph{metamodel} including entities, relations and attributes gathered from various sources such as text books, research papers, IREB, wikipedia, etc.
\end{itemize}
\end{Slide}

@@

\section{Methodology}
\subsection{Data Collection}
\begin{Slide}{Data Collection}
{\centering
\includegraphics[width=0.8\textwidth]{img/survey-screen-dump}
}
Q1 use? =   no, orally, also in writing\\
Q2 agree? = no, don't know, yes  \\
Answered by 15 swedish RE scholars (100\% response rate)\\
\url{https://github.com/bjornregnell/reqT-survey}

@@

\subsection{Data Analysis}
\begin{Slide}{Data Analysis}
\end{Slide}

\section{Results}
\subsection{Essentiality}
\begin{Slide}{Essentiality}
\end{Slide}

\section{Conclusion}
\subsection{Future Work}
\begin{Slide}{Future Work}
\end{Slide}

>>>>

\setbeamertemplate{footline}[frame number]
\title[What is essential? -- A research preview]{What is essential?}
\subtitle{\footnotesize -- A pilot survey on views about the requirements metamodel of reqT.org}
\author{Björn Regnell}
\institute{Lund University, Sweden}
\date{\href{http://refsq.org/2016}{refsq.org/2016}\\ \href{https://github.com/bjornregnell/reqT-survey}{github.com/bjornregnell/reqT-survey}}

@@

\item Make a survey among RE scholars
\pause
\begin{itemize}
\item How to quantify ''essentiality''?
\pause
\begin{itemize}
\item One possible quantification: \\ The more scholars that \Emph{agree} on a definition of a concept \\ and \\ the more scholars that \Emph{use} the concept, \\ the more \Alert{essential} is the concept.
\end{itemize}
\end{itemize}
\pause
\item Use the reqT.org metamodel as a basis for the survey
\end{itemize}
\end{Slide}

\section{Background}
\subsection{About reqT}
\begin{Slide}{What is reqT?}
\begin{itemize}
\item reqT is an open source requirements engineering tool developed in an \Emph{educational} context\\ Download from here: \url{http://reqt.org/} \\ \texttt{java -jar reqT.jar}
\item reqT aims to inspire \Emph{code-loving} cs students to learn more about RE through a \Emph{Scala}-internal DSL
\item has a metamodel with {\color{entityColor}{\bf entities}}, {\color{relationColor}{\bf relations}} and {\color{attributeColor}{\bf attributes}}\\ gathered from various sources such as \\ text books, research papers, IREB, wikipedia, etc.
\end{itemize}
\end{Slide}

@@

\section{Methodology}
\subsection{Data Collection}
\begin{Slide}{Data Collection}
{\centering
\includegraphics[width=0.8\textwidth]{img/survey-screen-dump}
}
{\small Q1 use =   \{no | used, but only orally | used, also in writing\}\\ Q2 agree = \{no, different meaning | don't know | yes, similar meaning\}  \\
Answered by 15 swedish RE scholars (100\% response rate)\\
\url{https://github.com/bjornregnell/reqT-survey}
}

@@

\subsection{Data Analysis}
\begin{Slide}{Data Analysis}
\textbf{Frequency analysis.} The degree of ''essentiality'' is characterized as the number of subjects that has responded that they (1) use the concept at least in an informal, non-persistent way, \textit{and} that they (2) use the concept in a similar meaning as in the definition in Appendix A.

\section{Results}
\subsection{Essentiality}
\begin{Slide}{Frequency Analysis}
\fontsize{6}{8}\selectfont

\begin{tabular}{l | p{0.33\textwidth} | p{0.30\textwidth} | p{0.25\textwidth}}
\textit{$n$} & \textit{Entities} & \textit{Attributes} & \textit{Relations} \\ \hline
\input{../proceedings/essential.tex}
\end{tabular}

\begin{Slide}{Essentiality Definition}
\begin{itemize}
\item If an ''essentiality threshold'' is chosen at $N/2$ then \\ only the $9$ concepts from row $n = 7$ and below are considered ''non-essential''
\item \Alert{More than 90\% of the 92 metamodel concepts have a majority of the subjects that use them and agree upon their definitions} 
\item Each concept has at least one subject that uses it and agrees with its definition. 
\end{itemize}

\section{Conclusion}
\subsection{Contribution \& Future Work}
\begin{Slide}{Conlusion}

\begin{itemize} 
\item Contribution
\begin{itemize} 
\item A way to quantify ''essentiality'' -- tested in a pilot survey
\item A set of potentially ''essential'' concepts \\ (according to 14 RE scolars in Sweden)
\end{itemize}
\end{itemize}

\begin{itemize} 
\item Future Work
\begin{itemize} 
\item More subjects for increased external validity
\item More questions on missing and alternative concepts
\end{itemize}
\end{itemize}
\end{Slide}
